TGI-spinal-power

### 2022-05-10 analysis/tgispine_lme_power.Rmd
creating density plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)
library(reshape2)

@@

# Summarise data per rating, per participant
df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*procedure*VAS, 
                    median, data = df)
```

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'cold' ,])
# then model warm VAS
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'warm' ,])
# model summaries
summary(model.cold)
summary(model.warm)
```
# Look at model assumptions
```{r}
# cold assumption
model.cold.assmup <- simulateResiduals(model.cold)
plot(model.cold.assmup)
```

```{r}
# warm assumption
model.warm.assump <- simulateResiduals(model.warm)
plot(model.warm.assump)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)
library(reshape2)
library(tidyverse)
library(plyr)

@@

# Summarise data per rating, per participant
df_sum <- aggregate(rating~ID*manipulation*condition*cold_location*procedure*VAS, 
                    median, data = df_VAS)
```

# Plotting data distributions to see what kind of model family is required
```{r}
ggplot(data = df_VAS) +
  geom_density(aes(beta, fill = manipulation), alpha = .5) +
  facet_wrap(~VAS)
```

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'cold' ,])
# then model warm VAS
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::betabinomial(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'warm' ,])
# model summaries
summary(model.cold)
summary(model.warm)
```
# Look at model assumptions
```{r}
# cold assumption
model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
plot(model.cold.assmup)
```

```{r}
# warm assumption
model.warm.assump <- simulateResiduals(model.warm, n = 1000)
plot(model.warm.assump)
```
